### 2017-05-11 paper/intro.tex
pass on intro

At large organizations, the alternative of renting cloud
services\footnote{List of popular hosting cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures to running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with modest
 or inexistent budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  For these cases, the use of commodity
hardware (\eg{}, existing workstations) is an attractive
solution for running tests.  The proliferation of
multi-core CPUs and the increasing popularization of testing
frameworks and build systems, which today provide mature support for
parallelization, enable test execution speedups through increased CPU
usage~(see Section~\ref{sec:modes}).  These two elements~---~demand
for cost-effective test execution and supply of relatively inexpensive
testing infrastructures~---~led us to investigate the usage of
parallelism to speed up test execution.

@@

This paper reports on an empirical study we conducted to analyze the
usage and impact of low-level parallelization to speed up testing
in open-source projects.  This is a relevant problem given the
tremendous popularity of open-source development and regression
testing research~\cite{yoo-harman-stvr2012}.  Note that
parallelization is complementary to other approaches to mitigate
testing costs such as (safe) test
selection~\cite{Rothermel:1997:SER:248233.248262} and continuous
integration~\cite{Saff:2003:RWD:951952.952340}.

The dimensions of analysis we considered in this study are (i)
potential, (iii) adoption, (iv) speedup, and (iii) issues.  The
dimension \emph{feasibility} measures the potential of parallelization
to reduce testing costs.  In the limit, parallelization would be
fruitless if all projects used short-running test suites or if the
execution cost was dominated by a single test case in the suite.  The
dimension \emph{adoption} evaluates how often existing open-source
projects use parallelization schemes and how developers involved in
costly projects (not using test suite parallelization) perceive this
technology.  It is important to measure resistance of practicioners to
the technology and to understand their reasons.  The dimension
\emph{speedups} evaluates the observed impact of
parallelization\Comment{~---~when used in selected open-source
  projects~---~} in running times.  Finally, the dimension
\emph{issues} reports the observed problems associated with running
tests in parallel.  For example, test flakiness, which is caused by
interference on shared state from non-deterministic executions of test
methods and classes.  We briefly summarize our findings in
the following.

@@

\vspace{1ex}\noindent\textbf{Speedups.}~We used two setups to measure
execution speedups.  In one setup we measured the speedups obtained on
projects that we knew a priori that ran their test suite in parallel
by default.  We did not change parallel configurations on that setup.
For comparison, we disabled parallel execution to obtain the running
time of a sequential execution.  In the other setup, we evaluated how
execution scales with the number of available cores in the machine.
\Mar{need to repeat those!}\Fix{Considering the first setup, results
  indicate that the average speedup of parallelization was
  \avgSpeedup{}x.  Although we found cases with very high speedups
  (\eg{}, 9.2x), we found some cases where speedups were
  insignificant.}

@@

>>>>

At large organizations, the alternative of renting cloud
services\footnote{List of popular hosting cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures for running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with modest
 or inexistent budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  For these cases, the use of commodity
hardware (\eg{}, existing workstations) is an attractive
solution for running tests.  The proliferation of
multi-core CPUs and the increasing popularization of testing
frameworks and build systems, which today provide mature support for
parallelization, enable\Comment{ test execution} speedups through increased CPU
usage~(see Section~\ref{sec:modes}).  These two elements~---~demand
for cost-effective test execution and supply of relatively inexpensive
testing infrastructures~---~led us to investigate the usage of
parallelism to speed up test execution.

@@

This paper reports on an empirical study we conducted to analyze the
usage and impact of low-level parallelization to speed up testing in
open-source projects.  This is a relevant problem given the tremendous
popularity of open-source development and regression testing
research~\cite{yoo-harman-stvr2012}.  Note that parallelization is
complementary to other approaches to mitigate testing costs such as
(safe) test
selection~\cite{Rothermel:1997:SER:248233.248262,gligoric-etal-issta2015}
and continuous integration~\cite{Saff:2003:RWD:951952.952340}.

The dimensions of analysis we considered in this study are (i)
potential, (iii) adoption, (iv) speedup, and (iii) issues.  The
dimension \emph{feasibility} measures the potential of parallelization
to reduce testing costs.  In the limit, parallelization would be
fruitless if all projects used short-running test suites or if the
execution cost was dominated by a single test case in the suite.  The
dimension \emph{adoption} evaluates how often existing open-source
projects use parallelization schemes and how developers involved in
costly projects (not using test suite parallelization) perceive this
technology.  It is important to measure resistance of practicioners to
the technology and to understand their reasons.  The dimension
\emph{speedups} evaluates the observed impact of
parallelization\Comment{~---~when used in selected open-source
  projects~---~} in running times.  Finally, the dimension
\emph{issues} reports the observed problems in running tests in
parallel (\eg{}, test flakiness~\cite{luo-etal-fse2014}).  We briefly
summarize our findings in the following.

@@

\vspace{1ex}\noindent\textbf{Speedups.}~We used two setups to measure
execution speedups.  In one setup we measured the speedups obtained on
projects that we knew a priori ran their test suite in parallel by
default.  We did not change parallel configurations on that setup.
For comparison, we disabled parallel execution to obtain the running
time of a sequential execution.  In the other setup, we evaluated how
execution scales with the number of available cores in the machine.
\Mar{need to repeat those!}\Fix{Considering the first setup, results
  indicate that the average speedup of parallelization was
  \avgSpeedup{}x.  Although we found cases with very high speedups
  (\eg{}, 9.2x), we found some cases where speedups were
  insignificant.}  Considering the second setup, results indicate that
\Fix{...}

@@

\newpage
